### 2024-11-06 analysis/analysis.qmd
feat(analysis): indicate class_n in classification studies
feat(analysis): begin analysis by class n

C_summary <- read.csv("C_summary.csv")

@@

>>>>

C_summary <- read.csv("C_summary.csv")
C_classes <- read.csv("C_study_class_n.csv")

C_summary <- merge(C_summary, C_classes)

@@

```
#### By class n = 2 vs. > 2
```{r}
C_summary$classes <- 0
C_summary[C_summary$n_classes < 3,]$classes <- "2"
C_summary[C_summary$n_classes >= 3,]$classes <- ">2"

m.cor <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n, # could also change to n_classes
                 studlab = studyREF, # unique_id
                 data = C_summary,
                 subgroup = classes,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Classification: Summary")

forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"),studlab = citekey)
